### 2021-12-16 documentos/pce.tex

\pce{} maps are defined as those quantum channels\R{A1} that \textit{nullify} Pauli strings. In the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$ with $\alpha=1,2,3$. The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,

@@

As mentioned above, \pce{} maps nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1,
\label{eq:definition:Pauli}
\end{equation}
with $\tau_{\vec \alpha}$ either $1$ or $0$.
\cpnote{Revisar aca lo que sigue}
Similar to the qubit case, not every operation with this form is a completely
positive trace perserving map. For the operation to be trace preserving, it is
easy to prove that $\tau_{\vec 0}=1$. On the other hand, constructing and
evaluating the conditions for complete positivity is involved and is the main
problem addressed in this paper. Moreover, these operations are by definition
diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$ basis.

>>>>

\pce{} maps are defined as those quantum channels\janote{David, los mapas PCE no son necesariamente canales cuánticos. Por esto, 
estás siendo incosistente en el uso de ``\pce{} maps'' en las líneas \lr{A1}, \lr{A2} y \lr{A3} del PDF. 
Especialmente, en la línea \lr{A1} seguro te estás refiriendo a todos los 
mapas, no sólo a los canales cuánticos} that \textit{nullify} Pauli strings. 
\janote{Por el comentario que hice antes propongo la siguiente reformulación:} 
\janote{
\pce{} maps are defined as positive trace-preserving (PTP) maps that 
\textit{nullify} Pauli strings.}
In the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$ with $\alpha=1,2,3$. The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,

@@

As mentioned above, \pce{} maps\R{A1} nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1,
\label{eq:definition:Pauli}
\end{equation}
with $\tau_{\vec \alpha}$ either $1$ or $0$.
\cpnote{Revisar aca lo que sigue}
Similar to the qubit case, not every operation with this form is a completely
positive trace perserving map. For the operation to be trace preserving, it is
easy to prove that $\tau_{\vec 0}=1$. On the other hand, constructing and
evaluating the conditions for complete positivity is involved and is the main
problem addressed in this paper. Moreover, these operations are by definition
diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$ basis.
